\large{Vipassana for Hackers} \\ \Huge{Paper Three: Why Meditate?} \\ \large\textit{Version 0.1}

### 2020-05-14 paper-three/paper-three.tex
Neuron speed via Carmack

\begin{itemize}
  \item posture
  \item sleep
  \item digestion (``Make sure to pay attention to your poops!'' first course)
  \item diet
  \item schedule
  \item health (activation / motivation)
  \item ethics (activation / motivation)
  \item your children: a. knowing how to meditate, b. cross-legged posture
  \item emotion (i.e. anger)
  \item dealing with death
  \item mundane sphere / productivity (21 lessons, seinfeld)
  \item unlearning obsessive / repetitive thought, enhancing creativity
  \item controlling unbounded sexuality without repression (louis c.k. joke?)
  \item clarity: in thought, work, planning
  \item Die Standing Up
  \item \url{https://www.pnas.org/content/early/2019/10/18/1909959116}
\end{itemize}

@@

\begin{itemize}
  \item reset frame of reference outside oneself, outside one's own lifetime: ``trees
    for god'' and obvious karma (sidu/booga smoking)
  \item Time: Nat Friedman's blog post?
  \item bible; ``a perfect set of rules''; nature itself <=> perception; ``perfect
    perception (vision)''; inner perception (sensation mirror) --- harris v. peterson
  \item clarification: ``isn't that what makes us human?'' (emotions) --- rather,
    what makes us animal
  \item ``How to Change Your Mind'' --- ego dissolution --- specific advantages?
  \item seeing oneself as aggregate and the path from singular => aggregate
    (neuroscience behind hemispheres)
\end{itemize}

>>>>

\begin{itemize}
  \item posture
  \item sleep
  \item digestion (``Make sure to pay attention to your poops!'' first course)
  \item diet
  \item schedule
  \item health (activation / motivation)
  \item ethics (activation / motivation)
  \item your children: a. knowing how to meditate, b. cross-legged posture
  \item emotion (i.e. anger)
  \item dealing with death
  \item mundane sphere / productivity (21 lessons, seinfeld)
  \item unlearning obsessive / repetitive thought, enhancing creativity
  \item controlling unbounded sexuality without repression (louis c.k. joke?)
  \item clarity: in thought, work, planning
  \item federated, p2p, distributed systems like blockchain / holochain attempt to circumvent
    structures of oppression and control -- what if corporations could be rebuilt from inside,
    one employee/stakeholder at a time such that ethics were inherent to the company's very
    existence?
  \item Die Standing Up
  \item \url{https://www.pnas.org/content/early/2019/10/18/1909959116}
\end{itemize}

@@

\begin{itemize}
  \item reset frame of reference outside oneself, outside one's own lifetime: ``trees
    for god'' and obvious karma (sidu/booga smoking)
  \item Time: Nat Friedman's blog post?
  \item Is it really possible? https://twitter.com/ID_AA_Carmack/status/1260698271422570497
    The “speed of thought” (neuron conduction speed) is only 110m/s, which isn’t that fast. 9 ms of latency just in your arm!
    https://www.youtube.com/watch?v=MeHoU-arXgY
  \item bible; ``a perfect set of rules''; nature itself <=> perception; ``perfect
    perception (vision)''; inner perception (sensation mirror) --- harris v. peterson
  \item clarification: ``isn't that what makes us human?'' (emotions) --- rather,
    what makes us animal
  \item ``How to Change Your Mind'' --- ego dissolution --- specific advantages?
  \item seeing oneself as aggregate and the path from singular => aggregate
    (neuroscience behind hemispheres)
\end{itemize}
